

## **Description of areas**

This experiment is located in four Atlantic forest protected areas: *Ilha do Cardoso State Park*, *Serra do Mar State Park* (Santa Virgínia/Itamambuca and Vargem Grande research base), and *Carlos Botelho State Park*. These areas also have differences in *Large Mammalian Herbivores* composition (LMH).

[**Ilha do Cardoso State Park**](https://www.saopaulo.sp.gov.br/conhecasp/parques-e-reservas-naturais/parque-estadual-ilha-do-cardoso/)

```{r, echo = FALSE}
library(knitr)
library(png)
```


On Cardoso Island we can only find the LHM White‐lipped peccary (*Tayassu pecari*). 

```{r, echo = FALSE, out.width="30%"}

myimages.car<-list.files("C:/Users/Yuri/Google Drive/Yuri/Mestrado/parcelas_biota/projeto/PPG/tese/analises/00_script/contributions/biota_shiny_dashboard/figures/ilha_cardoso/", pattern = ".png", full.names = TRUE)
include_graphics(myimages.car)

```


[**Serra do Mar State Park - Santa Virgínia/Itamambuca base**](https://www.infraestruturameioambiente.sp.gov.br/pesm/nucleos/santa-virginia/)

Santa Virgínia is considered the most faunated area of our experiment, and we can find there the LHMs Lowland tapir (*Tapirus terrestris*) and White‐lipped peccary (*Tayassu pecari*). 

```{r, echo = FALSE, out.width="30%"}

myimages.ita<-list.files("C:/Users/Yuri/Google Drive/Yuri/Mestrado/parcelas_biota/projeto/PPG/tese/analises/00_script/contributions/biota_shiny_dashboard/figures/santa_virginia/", pattern = ".png", full.names = TRUE)
include_graphics(myimages.ita)

```



[**Serra do Mar State Park - Vargem Grande base**](http://arquivos.ambiente.sp.gov.br/fundacaoflorestal/2012/01/1-Anexos.pdf)

On the opposite, Vargem Grande is the most defaunated area of our experiment, with low densities of the LHMs Lowland tapir (*Tapirus terrestris*) and White‐lipped peccary (*Tayassu pecari*). 

```{r, echo = FALSE, out.width="30%"}

myimages.vgm<-list.files("C:/Users/Yuri/Google Drive/Yuri/Mestrado/parcelas_biota/projeto/PPG/tese/analises/00_script/contributions/biota_shiny_dashboard/figures/vargem_grande/", pattern = ".png", full.names = TRUE)
include_graphics(myimages.vgm)

```



[**Carlos Botelho State Park**](https://www.saopaulo.sp.gov.br/conhecasp/parques-e-reservas-naturais/parque-estadual-carlos-botelho/)


On Carlos Botelho, we can only find the Lowland Tapir (*Tapirus terrestris*).

```{r, echo = FALSE, out.width="30%"}

myimages.cbo<-list.files("C:/Users/Yuri/Google Drive/Yuri/Mestrado/parcelas_biota/projeto/PPG/tese/analises/00_script/contributions/biota_shiny_dashboard/figures/carlos_botelho/", pattern = ".png", full.names = TRUE)
include_graphics(myimages.cbo)

```

